Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-11-06 paper/evaluation.tex
Fix section 5.1.
Fix references, add new text (marked in red).

\paragraph{Automatic segmentation pipeline.}
We use a state-of-the-art method to create a dense automatic segmentation of the data. Membrane probabilities are generated using a CNN based on the U-net architecture (trained exclusively on different data than the GP classifiers)~\cite{RonnebergerFB15}. The probabilities are used to seed watershed and generate an oversegmentation using superpixels. Agglomeration is then performed by the GALA active learning classifier with a fixed agglomeration threshold of 0.3~\cite{nunez2014graph}. We describe this approach in the supplemental material.

@@

\paragraph{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}. Focused proofreading performs graph analysis on the output from NeuroProof~\cite{neuroproof2013}, instead of our GALA approach. Therefore, for training our focused proofreading baseline, we replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities. We obtained the best possible parameters for NeuroProof by consulting the developers (Table~\ref{tab:parameters}). Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}) to compare only the classifier from Plaza's approach.

>>>>

\paragraph{Automatic segmentation pipeline.}
We use a state-of-the-art method to create a dense automatic segmentation of the data. Membrane probabilities are generated using a CNN based on the U-net architecture (trained exclusively on different data than the GP classifiers)~\cite{RonnebergerFB15}. The probabilities are used to seed watershed and generate an oversegmentation using superpixels. Agglomeration is then performed by the GALA active learning classifier with a fixed agglomeration threshold of 0.3~\cite{GALA2014}. We describe this approach in the supplemental material.

@@

\paragraph{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}. Focused proofreading performs graph analysis on the output from NeuroProof~\cite{neuroproof2013}, instead of our GALA approach. Therefore, for training our focused proofreading baseline, we replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities. We obtained the best possible parameters for NeuroProof by consulting the developers (Tab.~\ref{tab:parameters}). Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}) to compare only the classifier from Plaza's approach.

### 2017-11-06 paper/introduction.tex
Space squeezing.
Fix references, add new text (marked in red).

We train a classifier for split error detection with a convolutional neural network
(CNN). This takes as input patches of membrane segmentation probabilities, cell
segmentation masks, and boundary masks, and outputs a split-probability score. As we
must process large data, this classifier only operates on cell boundaries, which
reduces computation over methods that analyze every pixel. For merge errors, we
invert and reuse the split classification network, instead asking it to rate a
set of generated boundaries that hypothesize a split. %We compute
%corrections for both types of errors.

@@

This paper makes the following contributions.
%
First, we present a CNN-based boundary classifier for split errors, plus a merge
error classifier that inverts the split error classifier. This is used to
propose merge error corrections, removing the need to manually draw the missing
edge. These classifiers perform well without much training data, which is
expensive to collect for connectomics data.
%
Second, we developed a guided proofreading approach to correcting segmentation
volumes, and an assessment scenario comparing forced-choice interaction with
automatic and oracle proofreading.
%
Third, we present the results of a quantitative user study assessing
guided proofreading. Our method is able to reduce segmentation
error faster than state-of-the-art semi-automatic tools for both novice and
expert users.

>>>>

We train a classifier for split error detection with a convolutional neural network
(CNN). This takes as input patches of membrane segmentation probabilities, cell
segmentation masks, and boundary masks, and outputs a split-probability score. As we
must process large data, this classifier only operates on cell boundaries, which
reduces computation over methods that analyze every pixel. For merge errors, we
invert and reuse the split classification network, and ask it to rate a
set of generated boundaries that hypothesize a split. %We compute
%corrections for both types of errors.

@@

This paper makes the following contributions.
%
First, we present a CNN-based boundary classifier for split errors, plus a merge
error classifier that inverts the split error classifier. This is used to
propose merge error corrections, removing the need to manually draw the missing
edge. These classifiers perform well without much training data, which is
expensive to collect for connectomics data.
%
Second, we developed a guided proofreading approach to correcting segmentation
volumes, and an assessment scenario comparing forced-choice interaction with
automatic and oracle proofreading.
%
Third, we present the results of a quantitative user study assessing
guided proofreading. Our method is able to reduce segmentation
error faster than state-of-the-art semi-automatic tools for both novice and
expert users.
%
\CHANGED{Finally, we present the first standardized benchmark for proofreading in connectomics as an open research platform.}

### 2017-11-06 paper/related_work.tex
Several changes from the rebuttal.
Fix references, add new text (marked in red).

Karimov \etal~\cite{karimov_guided_volume_editing} propose guided volume editing, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This lets expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities. We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}).

>>>>

Karimov \etal~\cite{karimov_guided_volume_editing} propose guided volume editing, which measures the difference in histogram distributions in image data to find potential split and merge errors in the corresponding segmentation. This lets expert users correct labeled computer-tomography datasets, using several interactions per correction. To correct merge errors, the authors create a large number of superpixels within a single segment and then successively group them based on dissimilarities. We were inspired by this approach, but instead we generate single watershed boundaries to handle the intracellular variance in high-resolution EM images (Sec.~\ref{sec:methods}). \CHANGED{Recently, Zung \etal~\cite{error_detection_framework} report the successful application of 3D multiscale convolutional neural networks for error detection and correction as an additional post-processing step after segmentation. Their framework does not include humans in the loop and can be used as input to our proposed method.}

### 2017-11-06 paper/results.tex
Fix references, add new text (marked in red).

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Additional plots are available as supplemental material due to limited space.

@@

>>>>

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Additional plots and confirmatory data analysis are available as supplemental material due to limited space.

@@

\subsection{Proofreading in Connectomics Benchmark}

\CHANGED{We present the first proofreading benchmark for the field of connectomics as an open research platform. We include representative connectomics data with ground truth labels, all results and participant demographics from the interactive experiments by Haehn~\etal~\cite{haehn_dojo_2014}, our complete results from this paper, as well as standardized metrics for comparing different proofreading approaches at (link omitted for review). We hope that this framework facilitates future developments and allows comparisons for conquering the important proofreading problem in connectomics.}
